\OurTool{}: Integrative Probing Analysis of Nucleic Acids Empowered by Multiple Accessibility Profiles

### 2019-07-10 IPANEMAP-2019.tex
Updates from Overleaf

\section*{Funding}
This work, including AS and AD phD fellowships, has been supported by La Fondation pour la Recherche Medicale ([FRM
DBI20141423337]).
%\bibliographystyle{bioinformatics}
\bibliographystyle{nar}
%\bibliographystyle{natbib}%compa
\bibliography{biblio}

>>>>

\section*{Funding}
This work, including AS and DA phD fellowships, has been supported by La Fondation pour la Recherche Medicale ([FRM
DBI20141423337]).
%\bibliographystyle{bioinformatics}
\bibliographystyle{nar}
%\bibliographystyle{natbib}%compa
\bibliography{biblio}
